\chapter{Related Work}
\label{RW}
\textit{This chapter presents the related work within the field. It addresses the areas of dynamic and static taint tracking for Java, as well as other related platforms.}

\textcite{Haldar} has written a report about dynamic taint tracking for Java applications where the authors tried to solve the problem of correct user input validation. They built a tool that is independent of the web applications source code and the results from using the tool were proven to prevent code injection. \textcite{Haldar} evaluated the taint tracker on OWASP WebGoat \parencite{webgoat} but acknowledged that benchmarks of real-world web applications are needed to validate the implemented tools functionality. Their application supports taint tracking for the String class by adding a taint flag and altered the methods to propagate the taint. The tool \textcite{Haldar} implementation cannot be found for use for further evaluations.

Another implementation of a dynamic taint tracker for Java applications is Phosphor \parencite{phosphor} created by \textcite{BellJ.2014PIdd}. Phosphor was developed with the help of the Java bytecode manipulation library ASM \parencite{asm}. The application addresses taint tracking for primitives and arrays by introducing shadow variables. A shadow variable is a variable holding the taint flag for an un-instrumentable object. The shadow variable is injected into the application and placed next to each primitive and array. Each method in the application is also instrumented to pass shadow variables together with the un-instrumented object. Phosphor does however not support detainting of variables \parencite{BellJ.2014PIdd} which makes the application not suitable for finding code injection vulnerabilities. 

A third implementation of a dynamic taint tracker for Java applications is the Dynamic Security Taint Propagation \parencite{securityTaint} constructed with the help of the Java library AspectJ which enables aspect-oriented programming in Java \parencite{aspectj}. Dynamic Security Taint Propagation only propagates taint for the String, StringBuffer, and StringBuilder classes. The tool relies on aspect-oriented events that trigger the taint propagation, tainting data from sources, and assertions that ensure that tainted values do not pass through sinks. The application does however not support the ability to add or remove sources, sinks, and sanitizers. This lack of feature causes that the usability of the application becomes restricted to the current implementation.

In addition to dynamic taint trackers for Java applications, there exist dynamic taint trackers for other platforms. One of these is TaintDroid which is constructed for Android smartphones and aims to prevent privacy violations \parencite{EnckWilliam2014Taif}. TaintDroid uses a shadow memory which reduces the memory overhead of the application. \textcite{HsiaoS.W.2014PRse} has as well conducted further work on top of TaintDroid where is created a security scheme called PasDroid. PasDroid enables users to gain full control over the management of possible information leaks on Android devices.

There exist several static taint trackers, for example, FlowDroid by \textcite{ArztS.2014FPcf}. FlowDroid computes data flows for Java and Android applications. The static tracker is built with the help of the Soot framework \parencite{soot} providing analysis tools used to find possible vulnerabilities. The FlowDroid is evaluated in comparison to The AppScan and Fortify. The results show that the FlowDroid has a higher true positive and lower false positive rates.